Reprint Authors per Country

### 2019-10-22 analysis/001_kb_rp_pretest.Rmd

Country information about corresponding authors play a crucial role in open access funding [@Schimmer_2015]. The Web of Science contains data about this author role including affiliations, making it a valuable source to determine the productivity of corresponding authors per country ad journal.

@@

@@

A corresponding author lists at least two different countries, e.g., `UT=000400754000138`

@@

Potential issues: Only one affiliation is tagged as `RP` in `wos_b_2019.items_author_institutions`.

@@

More than one corresponding author is listed. For `UT_EID=000372645900002`, the Web of Science lists seven corresponding authors and four reprint adresses.

@@

Potential issue: As in Example 1, Only one affiliation is tagged as `RP` in `wos_b_2019.items_author_institutions`.

@@

Corresponding authors work in different countries. For `UT_EID=000372645900002`, the Web of Science lists two corresponding authors, one affilated with a Spanish, the other with a Portuguese institution.

@@

Potential issues: As in Example 1 and 2, only one affiliation is tagged with RP in `wos_b_2019.items_author_institutions`. Moreover, checking the WoS raw data reveals that the RP-author `14734495` is not affiliated with an Portuguese institution at all.

@@

1. Get all `FK_AUTHORS` tagged as `RP`, and store the result `rp_author_table`
2. From authors listed in `rp_author_table` obtain all countries of affilation and store them in `rp_countries_table`
3. Aggregate `rp_countries_table`

#### 1. Get all `FK_AUTHORS` tagged as `RP`, and store the result `rp_author_table`

>>>>

Country information about corresponding authors play a crucial role in open access funding [@Schimmer_2015]. The Web of Science contains data about this author role including affiliations, making it a valuable source to determine the productivity of corresponding authors per country and journal.

@@

<!--  why is issue of ex. 1 (multiple affiliations with differing author roles) not mentioned here?

Maybe add something like

4. Multiple country affiliations of the same author are listed with differing author roles

The first three issues are of a more conceptual nature, all leading to a situation where one article is associated with multiple countries of affiliation. One has to decide upon a way of handling them which has to be considered at the time of interpretation of the results. Two options for the mentioned issues are whole counting or fractional counting. For whole counting, each article is counted fully for any country of affiliation of any listed corresponding author, so that the number of articles in the single categories do not necessarily add up to the total number of articles any more. Fractional counting assigns a fraction of one article count to each corresponding author, leading to possible non-integer total article counts. The second issue is not much of a problem in our setting, if both authors are situated in the same country, since we are interested in the country of affiliation associated with an article. If, however, the corresponding authors' countries of affiliation differ as in issue 3, we again have to decide upon a counting scheme: do we count each country only once per article or multiple times if multiple corresponding authors work there? The fourth issue is rather a problem of data consistency. -->

@@

Potential issues: A corresponding author lists at least two different countries, e.g., `UT=000400754000138`. Additionally, only one affiliation is tagged as `RP` in `wos_b_2019.items_author_institutions`.

@@

@@

Potential issues: More than one corresponding author is listed. For `UT_EID=000372645900002`, the Web of Science lists seven corresponding authors and four reprint adresses. Furthermore, as in Example 1, only one affiliation is tagged as `RP` in `wos_b_2019.items_author_institutions`.

@@

@@

Corresponding authors work in different countries. For `UT_EID=000372645900002`, the Web of Science lists two corresponding authors, one affilated with a Spanish, the other with a Portuguese institution. As in Examples 1 and 2, only one affiliation is tagged with RP in `wos_b_2019.items_author_institutions`. Moreover, checking the WoS raw data reveals that the RP-author `14734495` is not affiliated with an Portuguese institution at all. <!--when I run the query it only shows 10 records, none of them has fk_author 14734495-->

@@

@@

1. Get all `FK_AUTHORS` tagged as `RP`, and store the result as `rp_author_table`
2. From authors listed in `rp_author_table` obtain all countries of affiliation and store them in `rp_countries_table`
3. Aggregate `rp_countries_table`

#### 1. Get all `FK_AUTHORS` tagged as `RP`, and store the result as `rp_author_table`
